### 2014-04-16 doc/uist14/iteration3.tex
iteration 3: gender neutral wording

During the second stage, when the user wants to use his head-motion for disambiguation, he will put his finger on the touchpad to enter a quasi-mode.  This gesture is inspired by observing users who tend to adjust their glasses for closer inspection.

In this mode, only one device has a solid indicator light on at a time. \bjoern{revisit prior sentence - there's a problem in the current technique in that the user doesn't know which targets are in the refinement set and which aren't.} The user can then tilt in the direction of the device he wishes to switch to. We calculate the direction of movement using a low-pass-filtered history of orientations, and look for devices that lie in that direction. Once a new device is selected, the frame of reference changes, and the user can repeat the process. Note that in reality, this is a completely smooth operation: it is possible to switch between multiple devices in one continuous motion. This is achieved by automatically adjusting the frame of reference to the currently lit device, but also creating a ``sticky" threshold so that the user is not constantly jumping between devices. \bjoern{This is called hysteresis or double thresholding.}

>>>>

During the second stage, when the user wants to use his head-motion for disambiguation, they will put their finger on the touchpad to enter a quasi-mode.  This gesture is inspired by observing users who tend to adjust their glasses for closer inspection.

In this mode, only one device has a solid indicator light on at a time. \bjoern{revisit prior sentence - there's a problem in the current technique in that the user doesn't know which targets are in the refinement set and which aren't.} The user can then tilt in the direction of the device they wish to switch to. We calculate the direction of movement using a low-pass-filtered history of orientations, and look for devices that lie in that direction. Once a new device is selected, the frame of reference changes, and the user can repeat the process. Note that in reality, this is a completely smooth operation: it is possible to switch between multiple devices in one continuous motion. This is achieved by automatically adjusting the frame of reference to the currently lit device, but also creating a ``sticky" threshold so that the user is not constantly jumping between devices. \bjoern{This is called hysteresis or double thresholding.}
